---
title: "Group21_Ikea"
author: "Group21"
date: "06/07/2021"
output:
  pdf_document:
    latex_engine: pdflatex
    number_sections: yes
  html_document:
    df_print: paged
  word_document: default
fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE, comment = NA)
```

## Ikea data analysis


```{r library}
library(tidyverse)
library(tinytex)
library(sjPlot)
library(jtools)
library(car)
library(reshape2)
library(kableExtra)
library(mice)

```
##Analysis

```{r glm}
ikea.sa<- read.csv("dataset21.csv")
imp<-mice(ikea.sa[,7:9],seed=1234)
ikea<-complete(imp)
stripplot(imp,pch=19,cex=1.2,alpha=.3)
```

##Introduction
Data set provided is from Ikea (Saudi Arabia), It is of interest to determine which properties of a furniture determine where the price is greater than 1000 riyals.

##Exploratory Analysis
#use category for graphical visualization

```{r exploratory}
options(digits = 4)
ikea.sa<- read_csv("dataset21.csv", na = "NA")
summary(ikea.sa[3:9]) %>%
kable(caption = '\\label{tab:summaries} Summary statistics for observations with chosen variables.') %>%
  kable_styling(latex_options = "hold_position")
#add price level>1000 :1
ikea.sa<-mutate(ikea.sa,price_level=if_else(price>1000,1,0))
ikea<-ikea.sa %>% mutate_all(~ replace_na(., 1))

#ikea<-ikea.sa %>% mutate_all(~ replace_na(., median(., na.rm = TRUE)))
#ikea$sellable_online<-ikea.sa$sellable_online
#<-ikea %>% group_by(width) %>% mutate_all(~ replace_na(., mean(., na.rm = TRUE)))
#ikea<-ikea.sa %>% group_by(height) %>% mutate_all(~ replace_na(., mean(., na.rm = TRUE)))


#GLM ?

glm.model.na <- glm( price_level~ sellable_online+other_colors+depth+height+width, data = ikea.sa, family = binomial(link = "logit"))

#glm.model.mean.all <- glm( price_level~ sellable_online+other_colors+depth+height+width, data = ikea, family = binomial(link = "logit"))


##glm.model <- glm( price_level~ other_colors+depth+height+width, data = ikea, family = binomial(link = "Identity"))

#x<-unique
#get_regression_table(glm.model.all)


glm.model.na%>%
  summary()



```

```{r }

#glm.model.mean.all%>%
  summary()
```
We have multiple NA values, But  Multiple imputation is out of scope for this analysis and therefore ignored.

##Formal Data Analysis



##Conclusions and Future Works

##Reference

