---
title: "Group21_Ikea"
author: "Group21"
date: "06/07/2021"
output:
  pdf_document:
    latex_engine: pdflatex
    number_sections: yes
  html_document:
    df_print: paged
  word_document: default
fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE, comment = NA)
```

## Ikea data analysis


```{r library}
library(tidyverse)
library(tinytex)
library(sjPlot)
library(jtools)
library(car)
library(reshape2)
library(kableExtra)
library(mice)

```


##Introduction
Data set provided is from Ikea (Saudi Arabia), It is of interest to determine which properties of a furniture determine where the price is greater than 1000 riyals.

##Exploratory Analysis
#use category for graphical visualization
```{r exploratory}
ikea.sa<- read.csv("dataset21.csv")
ikea.sa<-mutate(ikea.sa,price_level=if_else(price>1000,1,0))

summary(ikea.sa[3:10]) %>%
kable(caption = '\\label{tab:summaries} Summary statistics for observations with chosen variables.') %>%
  kable_styling(latex_options = "hold_position")

```

```{r glm }
#interpolation for missing values
imp<-mice(ikea.sa[,7:9],seed=1234)
stripplot(imp,pch=19,cex=1.2,alpha=.3)
imp<-mice(ikea.sa[,3:10],seed=1234)
ikea<-complete(imp)


#add price level>1000 :1
ikea.sa<-mutate(ikea.sa,price_level=if_else(price>1000,1,0))

fit<-with(imp,glm(price_level~sellable_online+other_colors+depth+height+width),family=binomial(link="logit"))
fit1<-pool(fit)
summary(fit1,conf.int = TRUE,level=0.95)

#reject insignificant explanatory variables. fit into new model

fit<-with(imp,glm(price_level~depth+height+width),family=binomial(link="logit"))
final<-pool(fit)
summary(final,conf.int = TRUE,level=0.95)
```g37 tx
We have multiple NA values, we use  Multiple imputation to add meaningful values to the dataset. this allows us to retain half the dataset and perform analysis on it more effectively.

##Formal Data Analysis


##Conclusions and Future Works

##Reference

